Is It Possible to Steal Money Through USB-C?

### 2020-12-22 WOOT/Files/badusb.tex
add outline

\section{\tool}

\subsection{Motivation}
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take use of the \textit{default trust} given by computers to HIDs, pretend normal USB devices as HIDs and uitilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lacking of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

@@

\subsection{Implementation}
The implementation of \tool extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing). We implemented the QR-Code extraction agent from scratch. The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.

>>>>

\section{\tool}
\label{sec:badusb}
\subsection{Motivation}
\noindent\outline{Limitation of Rubber Ducky}\\
\outline{Our functionality different mode listing?}\\
\hongyi{The following mode is to be further decided}
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
Many of these take use of the \textit{default trust} given by computers to HIDs, pretend normal USB devices as HIDs and uitilize USB protocol to perform attacks. 
However, these attacks suffer from various drawbacks:
\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks, which makes the attacks less effective;
\ding{183} accurate attacks couldn't be performed due to lacking of user interface (UI).
Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.

@@

\subsection{Implementation}
\noindent\hongyi{The following mode is to be further decided}\\
\outline{DETAIL of each mode}\\
\outline{Automatic Scripting Mode}\\
\outline{Remote Control Mode}\\
\outline{OCR/QR Recognition Mode}\\
The implementation of \tool\ extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing). We implemented the QR-Code extraction agent from scratch. The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.

### 2020-12-22 WOOT/Files/experiment.tex
add new convention about label, combine member's .tex,
add outline

\section{Experiment}
\label{section:experiment}

Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.

>>>>

\section{Experiment}
\label{sec:experiment}
\noindent\outline{Case Study: Sharing Power Bank}\\
\outline{Overview}\\
\outline{Attack Procedure(how to  get picture, etc.)}\\
\outline{Security Issues against APPLE/Android...etc.}\\
Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.

### 2020-12-22 WOOT/Files/related_work.tex
add outline

\section{Related Work}
\label{sec:related_work}
In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
\subsection{USB Attack Security}
USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}. USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s). Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.

@@

>>>>

\section{Related Work}
\label{sec:related_work}
\hongyi{Move the stuff about USB protocol to Background}\\
In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
\subsection{USB Attack Security}
USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}. USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s). Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.

@@

Tian, Jing, et al.\cite{sok} have made a brief overview of the defense countermeasures over four layers attack in the article. For attacks against human-layer problems, \cite{cmu}raise people's awareness of social engineering,\cite{Ironkey},\cite{Kanguru},\cite{diwan2014complete} prevent the data from being stolen by on-device encryption, \cite{butler2010kells},\cite{tian2016provusb} provide host authentication and monitor data flow to record potential malicious IO behaviors. [9] block physical connections to defense. In application layer,modification over OS and driver are adapted. \cite{pham2010optimizing} and \cite{OPSWAT} harden  host system to prevent automatic execution of malicious code. GoodUSB \cite{tian2015defending} offers strict access control, with the system soliciting desired functionality from the user and blocking other functionality for a device. Ghost \cite{poeplau2012honeypot} simulates as a USB device to detect if the host has malicious code injection. In transport layer, FirmUSB \cite{hernandez2017firmusb} and VIPER \cite{li2011viper} check the firmware of the device to ensure its safety. Fuzzing is a method of detecting vulnerabilities by providing unexpected input to the target system and monitoring for abnormal results. Some related work,\cite{jodeit2010usb},\cite{schumilo2014don},\cite{patrick2017potus},focuses on using USB fuzzing approach to detect potential bugs in USB driver. USBFirewall \cite{johnson2017protecting} protects the host based on error detection of USB communication packages. In some related work, \cite{tian2015defending},\cite{angel2016defending}, e. g, VM is deployed in host to interact with the USB device for malicious behavior detection. In physical layer, some related work like \cite{bates2014leveraging} consider anti-fingerprinting ,and some others like \cite{neugschwandtner2016transparent} consider data encryption on USB bus.
